### 2015-05-14 background.tex
cutting space in bg

Example~\ref{fig:data_race_example} presents multiple data races that \whoop automatically found in the generic\_nvram Linux char driver (see \S\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can read/write access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order resulting into nondeterministic behavior.

>>>>

Example~\ref{fig:data_race_example} presents multiple data races that \whoop automatically found in the generic\_nvram Linux char driver (see \S\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order.
